---
title: "ToothGrowth"
output: 
  html_document:
    keep_md: true
---
_Data Science / Statistical inference / Peer Assessment 2_   
_Andrey Komrakov_  
_Dec 27 2015_  
_Source files github.com/kolfild26/statinference_  

### Setting up and loading packages
```{r settings, results='hide', message=F, warning=F}
library(datasets)
library(dplyr)
library(ggplot2)
library(knitr)
Sys.setlocale("LC_TIME", "English")
```

### Data Summary
```{r }
ggplot(ToothGrowth, aes(x=dose, y=len, color=supp)) +
  geom_point(alpha=.5, size=5) +
  stat_smooth(method=lm, se = FALSE) +
  theme(legend.position=c(1,0), legend.justification=c(1,0))+ 
  ggtitle("Tooth lendth against dose by supplement")

summary(ToothGrowth)

```

### Perfoming T-test to investigate the effect of to supplements

```{r }
t.test(len ~ supp, data = ToothGrowth)

```

```{r pvalue, echo=FALSE}
pval <- round(t.test(len ~ supp, data = ToothGrowth)$p.value, 3)
```

### Conclusion
Based on the assumption of independent samples, having got the p-value = `r pval` we can accept the null hypothesis of equivalence of the means of two types of supplement. As the difference in means is not significant in terms of 95% probability, then one can say that both supplements have a similar effect.
